Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-02-01 paper/paper.tex
more on algorithm

{\color{red}
MISSING
\begin{itemize}
\item cross-validation scheme
\item analysis of penalty tradeoff (CV scheme for that?)
\item mentioning of control methods in methods. Trace norm, sparse group sparsity. Anything else? ENET?
\end{itemize}
}

>>>>

\paragraph{Hyperparameter optimization.}
{\color{red} NEEDS EMBELLISHING}
We perform nested cross-validation to obtain optimal hyperparameters. 
In order to analyse their effect in detail, we split our analysis into two 
parts.
\begin{enumerate}
\item In the first part, we optimize the trade-off between the different hierarchy levels as well as the global penalty level for maximal prediction.
\item in the second part, we select the optimal global penalty level for 
given trade-off ratios.
\end{enumerate}

\paragraph{Control methods}
{\color{red} needs embellishing}
We evaluate our tree structure against other commonly used structured sparse
penalties.
